Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-04-20 paper.tex
addressing comments in the experiments

In the first experiment, forecasting methods have been applied to the whole dataset. All the pre-sales features have been considered, also including the categorical ones, which make harder to process the instances and build the different models. SVM for instance, must previously transform these categories into numbers in order to deal with the data, which means the creation of a different (and new) variable per possible value. Thus, in the case of editorial or collection this would imply the definition of hundreds of new variables.
% Antonio - Sam, verify this, please

@@

In this second experiment, different feature selection processes have been applied.

***TODO***: The aim of these techniques is to reduce the number of features to consider...
% Antonio - TODO: explain the aim of FS in these experiments.

>>>>

In the first stage of the experiments, forecasting methods have been applied to the whole dataset. All the pre-sales features have been considered, including the categorical ones, which make it harder to process the instances and build the different models. SVM for instance, must previously transform these categories into binary variables in order to deal with the data, which means the creation of a different (and new) variable per each possible value. Thus, in the case of editorial or collection this would imply the definition of hundreds of new variables.
% Antonio - Sam, verify this, please
% Sam - reviewed and fixed

@@

In the second stage of the experiments, different feature selection methods have been applied. The aim of these methods is to reduce the number of features considered in developing the forecasting models which consequently simplify the complexity of the models, improve their interpretability and decrease the training time. The simpler models generated after performing feature selection could give the decision maker a better insight on the underlying process by identifying the more influencing variables.

% Antonio - TODO: explain the aim of FS in these experiments.
% Sam : Done
